Metrics

### 2023-12-01 src/metrics.Rmd
Regen plots

# Create cod with counts
cod_remap <- list()
for (cod_col in causes_col) {

@@

    # Add label for cod
    cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")
}

@@

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.055, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

>>>>

# Create cod with counts
cod_remap <- list()
cod_counts <- list()
for (cod_col in causes_col) {

@@

    # Add label for cod
    cod_remap[[cod]] <- paste0(cod_label, "\n(n=", ncod, ", ", pcod_label, "%)")

    # Store cod count data
    cod_counts[[cod]] <- ncod
}

@@

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.055, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.1, 0.75) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        plot.margin = margin(t = 16, b = 12, l = 12, r = 12),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )
